On $K_2$-analogue of Serre problem for $\SL_4$

### 2018-09-25 paper.tex
Minor

\subsection{Steinberg groups and relative Steinberg groups}

@@

\begin{rem} It is clear that the maps $\sigma(\varpi)$, $\sigma(-\varpi)$ are uniquely determined by~\eqref{eq:sigmadef}, so at most one $\sigma$-pair may exist for any given $\varpi$. However, since we have no direct description of the set of relations between the elements of $\mathcal{X}(\varpi)$, we cannot a priori claim that maps $\sigma(\pm\varpi)$ with the property~\eqref{eq:sigmadef} exist.
\end{rem}

@@

\subsection{Factorization theorem} 
For a ring $R$ we denote by $\Sym(\Phi, R)$ the subgroup of $\St(\Phi, R)$ generated by Steinberg symbols $\{a, b\}_\alpha$, $a, b \in R^*$. 
 If $\rk(\Phi)\geq 2$ it is clear that $\Sym(\Phi, R)$ is a central subgroup of $\St(\Phi, R)$ contained in $\K_2(\Phi, R)$. 
Denote by $H(R) \subseteq \St(\Phi, R)$ the composite of the two subgroups $\Sym(\Phi, R)$ and $\UU(\Phi^+, R)$.
It is clear that $H$ is a functor on the category of commutative rings.

@@

Denote by $V_0$ the set $\St(\Phi, A[t]) \times H(A[t, t^{-1}]) \times \St(\Phi, A[t, t^{-1}], M[t, t^{-1}])$. 
We define an equivalence relation $\sim$ on $V_0$ as the minimal equivalence relation generated by the following 3 elementary transformations:
\begin{enumerate}
 \item $(a \cdot j_+^*(p), b, \beta) \sim (a, H(p) \cdot b, \beta)$, where $p$ is an element $H(A[t])$;
 \item $(a \gamma, b, \beta) \sim (a, b, ?(\gamma)^b \beta)$, where $\gamma$ is an element of $\St(\Phi, A[t], M[t])$;
\end{enumerate}

>>>>

\subsection{Steinberg groups and relative Steinberg groups}
\subsection{Relative Steinberg groups}

@@

\begin{rem} It is clear that the maps $\sigma(\varpi)$, $\sigma(-\varpi)$ are uniquely determined by~\eqref{eq:sigmadef}, so at most one $\sigma$-pair may exist for any given $\varpi$. However, since we have no direct description of the set of relations between the elements of $\mathcal{X}(\varpi)$, we cannot a priori be sure that formulas~\eqref{eq:sigmadef} specify well-defined maps between $N(\varpi)$ and $N(-\varpi)$.
\end{rem}

@@

\subsection{Factorization theorem} 
For a ring $R$ we denote by $\Sym(\Phi, R)$ the subgroup of $\St(\Phi, R)$ generated by Steinberg symbols $\{a, b\}_\alpha$, $a, b \in R^*$. 
 If $\rk(\Phi)\geq 2$ it is clear that $\Sym(\Phi, R)$ is a central subgroup of $\St(\Phi, R)$ contained in $\K_2(\Phi, R)$. 
Denote by $H(R) \subseteq \St(\Phi, R)$ the composite of the two subgroups $\Sym(\Phi, R)$ and $\UU(\Phi^+, R)$.

@@

Denote by $V_0$ the set $\St(\Phi, A[t]) \times H(A[t, t^{-1}]) \times \St(\Phi, A[t, t^{-1}], M[t, t^{-1}])$. 
We define an equivalence relation $\sim$ on $V_0$ as the minimal equivalence relation generated by the following 3 elementary transformations:
\begin{enumerate}
 \item $(a \cdot j_+^*(p), b, \beta) \sim (a, H(p) \cdot b, \beta)$, where $p$ is an element $\UU(\Phi^+,A[t])$;
 \item $(a \gamma, b, \beta) \sim (a, b, ?(\gamma)^b \beta)$, where $\gamma$ is an element of $\St(\Phi, A[t], M[t])$;
\end{enumerate}
